\section{Introduction}
\label{sec-intro}

\Cyclus \cite{cyclus_v1_0,cyclus_v1_2,huff_fundamental_2016} is the first truly agent-based 
\cite{jennings2000agent} nuclear fuel cycle simulator. 
New technologies, while exciting, often pose unforeseen challenges.
\Cyclus is no exception to this rule.  This paper answers the questions,
\emph{``What precisely is an agent in a nuclear fuel cycle context?''} and 
\emph{``What features of simulation can be abstracted away to ease the burden 
on nuclear fuel cycle researchers?''}

The genesis of \cyclus lies in the desire to 
treat mass balances as discrete, model facilities individually rather than as 
a fleet, and to be able to quantitatively compare the effects of changing the 
fidelity of the facilities themselves. These goals necessitate a large degree of 
sophistication on the part of the simulator infrastructure.  Resource exchange
must be handled in a generic and dynamic way as opposed to being hard-coded 
for specific commodities. Simulations must be inherently comparable, which involves 
storage infrastructure that is designed around this need. Agents must be able 
to communicate with one another and learn about the environment in which they 
exist. Additionally, agents must be able to be dynamically deployed and the set of 
available agent models may not be collected until run time. 

What sets nuclear fuel cycle simulation apart from traditional agent-based simulations 
is the high degree of agent specialization. Standard agent-based simulators
are characterized as having a few types of agents, often only one and 
almost always less than five \cite{taylor2014agent}. The agent types are then 
specialized 
when they are instantiated \emph{in situ}. This model is insufficient for 
nuclear fuel cycle applications.  For example, it would be unwise to have a single facility model 
that represents both enrichment and reactors, called \code{EnrichmentOrReactor},
that decides via a switch how it behaves when it is deployed. It is much 
more natural to have two models, \code{Enrichment} and \code{Reactor}, 
that implement their own physics calculations independently.

\Cyclus enables agent specialization along two separate axes. The first defines 
an agent as an \emph{entity} that determines its role in the 
nuclear fuel cycle. There are three kinds of entities: \emph{regions} that 
represent geographic and governmental concerns, \emph{institutions} 
that manage other agents, and \emph{facilities} that implement 
physics calculations and are usually in charge of resource management.

The other axis of agent specialization distinguishes among who 
writes the model, who sets up the model for potential use in a simulation,
and who actually deploys concrete representations of the model.
At the highest level are \emph{archetypes} whose behavior is parameterizable. 
Archetypes are software implementations
of physical, chemical, economic, and political models.
For example, a \code{Reactor}  archetype may be 
parameterized by a target burnup. Authors of these highly reusable models 
are known as \emph{archetype developers}. Archetypes are in turn 
\emph{configured} into \emph{prototypes}. A prototype is a copy 
of the archetype but with all parameterizations set to concrete 
values. Hence, a \code{Reactor} with a burnup of 42 MWd/kg is a 
prototype. Configuring archetypes into prototypes is done by the \cyclus user 
in the input file. Configuration requires no underlying knowledge of 
how the archetype is implemented, though that often helps.
Finally, when prototypes are copied and \emph{deployed} in the simulation 
they become \emph{agents}. This usage of the term `agent' to mean 
the \emph{in situ} object is consistent with other agent-based
literature \cite{macal2005tutorial}.  Agent deployment happens exclusively via 
\cyclus itself; manual deployment of agents is not allowed.
Archetypes that wish to deploy agents must \emph{schedule} their building
and decommissioning.

Archetype development is one of the most difficult aspects of agent-based
simulation. Physical models be determined, implemented, and 
validated. Moreover, this is where agents interface with the 
\cyclus kernel itself. The dynamism of agent-based simulation 
coupled with the need to have traditional simulator features
(such as restart and validation) creates a complex interface with the kernel.
Archetype development would be much simplified if saving and 
loading from disk and communicating with other agents were 
never a concern, though such a simulator would be of marginal use.
Due to these complexities, archetype development in \cyclus
has historically been difficult. Obtaining a working archetype
that performed no physics calculations from scratch would 
take novice developers upwards of two weeks effort.  The complexities
that lead to such a high bar are emblematic not just of \cyclus,
but of any agent-based nuclear fuel cycle simulator.

Informal polling by the \cyclus team over the years
showed that a new developer circa \cyclus v0.1
took 2+ weeks to get a working `do-nothing' archetype. This is obviously 
too long because most researchers do not have two weeks of time `just to try 
something out.' By \cyclus v0.3 the do-nothing development time had been reduced 
to approximately one business week. In \cyclus v0.4, this time became about 3 days.
As of \cyclus v1.0, this finally was reduced down to 1 - 4 hours, which meets
appropriate expectations for someone attempting \cyclus as a first time archetype 
developer.

These dramatic development time reductions were caused by two forces:
clarification of the archetype abstraction and explicit tools to help with 
archetype creation. While the region-institution-facility hierarchy was established 
early on, the formulation of this hierarchy in an agent-based paradigm took much 
longer to firmly establish.  Once this notion had been refined, attention turned to 
simplifying \Cyclus archetype development.
For a long time in the history of this simulator and its predecessors, such as 
\gls{GENIUSv2} \cite{oliver_studying_2009}, tools to help make archetypes were 
absent.
The addition of archetype tools described in this paper made development significantly more efficient.

The archetype development tools provided by \cyclus must overcome a variety of 
technical hurdles in order to make archetype development accessible.  These 
include, but are not limited to, the lack of reflection in the C++ programming language,
the desire to support multiple database formats, automatic validation of input files,
special mechanisms for handling resource exchange and inventory persistence, 
and the somewhat complex interface required to support the snapshotting and 
restart of simulations. Such concerns are basic to \cyclus operation but 
ancillary to the physics, chemistry, and economics being modeled by an 
archetype developer.
The minutia should `just work' since it is not a core part of a fuel cycle model.

This paper describes the strategies, efforts, interfaces,
and implementations that considerably reduce the complexity  
an archetype developer must deal with directly. This has been 
found to reduce development effort for simple agents down to a couple 
of hours for novices. Expert archetype developers realize further 
reductions down to a couple of minutes. This has has been accomplished 
without sacrificing an iota of simulation fidelity. Since such 
problems proliferate among agent-based simulators, the methods described here apply beyond \cyclus.
Though such methods sometimes dive into 
computer science and agent-based modeling details, they are always implemented
with the express goal of making fuel cycle simulation 
simpler, easier, faster, more expressive, and validated.

This paper proceeds by first providing a more detailed motivation 
in \S \ref{sec-motive}. Then, \S \ref{sec-methods} describes
methods and mindsets that are used to ease archetype development.
Some of these are high-level design strategies, while others are software 
interfaces that 
provide the correct fuel cycle agent abstractions. 
\S \ref{sec-impl} describes the underlying algorithms and usages
for those methodologies, which also require concrete implementations.
Lastly, \S \ref{sec-conc} provides final remarks and illustrates
potential future directions for \cyclus archetype development.
